Verifying Demonstrations

### 2017-08-31 properties.tex
Improves order or properties
Uses term blockchain instead of t-poset

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to verify that each proof is indeed related to the 
event.
We must associate the proof to the event both spatially (the correct location) 
and temporally (it is related to the time-interval of the event).
We can essentially divide it into the following requirements:
\begin{requirements}[\ref*{EligibilityVerif}.]
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}

\mode<presentation>{%
\begin{frame}
  \begin{requirements}[V\ref*{EligibilityVerif}.]
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}
}

@@

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Temporal eligibility]
      \begin{itemize}
        \item We need a partially ordered set (poset).

@@

        \item There is a mechanism that provides this property: a blockchain.
        \item There are also other structures, e.g.\ a directed 
          graph~\cite{BlockchainFreeCryptocurrencies}.
      \end{itemize}
    \end{idea}
  }
  \only<3>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included (duh!).
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<4>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
protest, then the relation will guarantee that \(p_A, p_B\) were created before 
the end of the protest.
Then we know that they cannot have been created after the event.

@@

They can use an older value (pick one from the history of the \ac{tposet}) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval, i.e.\ possibly before the protest.

@@

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane attends the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the \ac{tposet} during the protest.
\end{remark}

@@

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.Proof
        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
        %[.tsig {$t_s''$} ]
        ]
        {\dots}
        [.{wsig} {\dots} ]
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
      %[.tsig {$t_s''$} ]
      ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

@@

  \begin{idea}[Proof privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.
      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    The proof itself is a sort of receipt.
  \end{remark}

@@

  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.
    \end{itemize}
  \end{idea}
\end{frame}
}

\begin{frame}
\mode<presentation>{%
  \begin{idea}
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use it 
        to verify that she participated.

      \item We need a signature scheme that cannot reproduce the same signature 
        when run on the same inputs.

@@

Say that Alice submits her proof and stores the hash of the head of the 
\ac{tposet} after her proof is included.
Now she can remove her proof and just keep the hash to verify that her proof is 
still there.
She can also remove her signature key, so that Eve cannot use it to reproduce 
the signature using the same inputs.

>>>>

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to verify that each proof is indeed related to the 
event.
We must associate the proof to the event both spatially (the correct location) 
and temporally (it is related to the time-interval of the event).
We can essentially divide it into the following requirements:
\begin{requirements}[\ref*{EligibilityVerif}.]
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}

\mode<presentation>{%
\begin{frame}
  \begin{requirements}[V\ref*{EligibilityVerif}.]
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}
}

@@

\mode<presentation>{%
  \only<1,2>{%
    \begin{idea}[Temporal eligibility]
      \begin{itemize}
        \item We need a partially ordered set (poset).

@@

        \item There is a mechanism that provides this property: a blockchain.
        \item There are also other structures, e.g.\ a directed 
          graph~\cite{BlockchainFreeCryptocurrencies}.
      \end{itemize}
    \end{idea}
  }
  \only<3>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included.
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<4>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          blockchain, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the blockchain \emph{in (time-wise) relation to the event}.
In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
protest, then the relation will guarantee that \(p_A, p_B\) were created before 
the end of the protest.
Then we know that they cannot have been created after the event.

@@

They can use an older value (pick one from the history of the blockchain) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval, i.e.\ possibly before the protest.

@@

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane attends the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the blockchain during the protest.
\end{remark}

@@

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.Proof
        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
        %[.tsig {$t_s''$} ]
        ]
        {\dots}
        [.{wsig} {\dots} ]
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
      %[.tsig {$t_s''$} ]
      ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the blockchain.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

@@

  \begin{idea}[Proof privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.

      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item The proof itself is a sort of receipt.

@@

      \item If Eve compromises Alice's device, she can use it to verify that 
        she participated.

      \item We need a signature scheme that cannot reproduce the same signature 
        when run on the same inputs.
    \end{itemize}
  \end{remark}
\end{frame}
}

\begin{frame}
\mode<presentation>{%
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the blockchain.
      \item She removes the proof and signature key.

@@

Say that Alice submits her proof and stores the hash of the head of the 
blockchain after her proof is included.
Now she can remove her proof and just keep the hash to verify that her proof is 
still there.
She can also remove her signature key, so that Eve cannot use it to reproduce 
the signature using the same inputs.
